Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-10-17 crowdsource/article.tex
improve mini-text 1

A partial correlation approach \cite{sutera2014simple}  is a simple yet effective
solution to the problem of connectome inference in calcium imaging data.
This winning approach of the Connectomics challenge consists of two steps.
First, time-series are processed using standard
signal processing filters in order to : (i) remove noise mainly due to
fluctuations independent of calcium, calcium fluctuations independent of
spiking activity, calcium fluctuations in nearby tissues that have been
mistakenly captured, or simply by the imaging process ; (ii) to account for
fluorescence low decay ; and (iii) to reduce the importance of high global
activity in the network. Secondly, inferring the degree of association between
neurons is then made with partial correlation statistics, the inverse of the
correlation matrix. This statistical measure has the property to filter
indirect associations between neurons and gives a high degree of association
between directly connected neurons.

>>>>

A partial correlation approach \cite{sutera2014simple}  is a simple yet
effective solution to the problem of connectome inference in calcium imaging
data. This partial correlation statistics, the inverse of the correlation
measure, has  the property to filter indirect associations between neurons and
gives a high degree of association between directly connected neurons. The
winning solution of the Connectomics challenge combines two main steps:
(i) data are pre-processed using signal processing filters; (ii)
the network is infered through partial correlation. The pre-processing step
highly improves the infered network by removing noise and taking into account
specifities of the fluorecense signals.
